Summarize Growth Curves

#### Description
This function finds the parameters that describe the input data’s growth for a plate of growth curves.
It does so by fitting the logistic curve to your growth curve measurements.

#### Usage
<pre><code>
SummarizeGrowthByPlate(plate, t_trim = 0, bg_correct = "min",
plot_fit = FALSE, plot_file = "growthcurver.pdf")
</code></pre>

#### Arguments
plate A data.table with at least two columns. One column contains timepoints that
measurements were taken (e.g., hours) and must be named "time". An optional column can be included called "blank" that contains the blank readings for background correction (make sure to select the "blank" bg_correct option if you provide a blank column). Each remaining column contains the absorbance readings from a single well in a plate.
t_trim Measurements taken after this time should not be included in fitting the curve.
If stationary phase is variable, this may give you a better fit. A value of 0 means no trimming. Defaults to no trimming (0).
bg_correct The background correction method to use. No background correction is performed for "none". Specifying "min" subtracts the smallest value in a column
from all the rows in that column, and specifying "blank" subtracts the values from the blank vector from the data_n vector.
plot_fit TRUE if you want to generate a pdf file that plots all columns provided in the
plate along with the growthcurver’s fit. The default value is FALSE, which generates no plots.
plot_file The name of the file to save the plots to if you set plot_fit to TRUE. The default file is called "growthcurver.pdf".

#### Details
The logistic curve equation is
N t =
N 0 K
N 0 + (K − N 0 )e −rt
where N t is the number of cells (or the absorbance reading) at time t, N 0 is the initial cell count (or
absorbance reading), K is the carrying capacity, and r is the growth rate.

The fitness proxies returned are the parameters of the logistic equation and the area under the curve
(a measure that integrates the effects of N 0 , K, and r). See gcfit for more documentation on these.

This method expects that your data adhere to a particular format.

* The data are provided in a data.frame
* One column in the data.frame is named "time" and contains the time measurements (e.g.,
hours).
* Each remaining column contains the readings from a single well in a plate reader. The name
of the column will be used to identify the sample in the output data.
* There are no missing values or non-numeric data in the data.frame.

#### Value
A data.table containing the summary metrics and residual error from the fit of the logistic curve to
the data. The names of the input columns are used to identify each well (or sample).

#### See Also
See the accompanying Vignette for an example of how to use and interpret SummarizeGrowthBy-
Plate. bit.ly/1p7w6dJ

#### Examples
```{r}
#Get the summary metrics for the entire plate of sample data provided
#with the Growthcurver package
#First, load the example data provided with Growthcurver. Note that there is
#a column named "time" -- this is necessary for Growthcurver to know which
#column contains the time measurements. In this dataset, the repeated
#measurements from a single well in a plate are given in a column of data.
myPlate <- growthdata
names(myPlate)
```


```{r}
#Next, do the analysis for all the columns.
summary_plate <- SummarizeGrowthByPlate(plate = myPlate)
#The output is a data frame that contains the information on the best
#fit for each column of data.
head(summary_plate)
# Use head to display just the first few rows
```
